---
title: 'Report: Missing data'
author: "Steve and Jonathan"
date: " `r as.Date(Sys.time())` "
output:
  html_document:
    fig_caption: yes
---


```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = FALSE
	, warning = FALSE
	, message = FALSE
	, fig.width = 10
	, fig.height = 10
	, fig.align="center"
	, results = "asis")
options(width = 12)

library(ggplot2)
theme_set(theme_bw() +
	theme(panel.spacing=grid::unit(0,"lines")))

library(forcats)
library(ggpubr)

library(dplyr)
library(DT)
library(scales)
library(dotwhisker)
library(ggstance)
library(corrplot)
library(lme4)
library(splines)

load("analysis_variables.rda")
load("overall_missing_tables.rda")
source("../funs/ggplot_theme.R"); ggtheme()

```

## Missing data

-  $2002 - 2005$ are excluded from the analysis
- APHRC categorized missing data as follows ([See](./docs/ddi-documentation-english-54.pdf)):
	- `missing:impute`: Missing information and can be imputed
	- `refused`: Assigned to any variable where the respondent refused to answer or participate
	- `Don't know`: Assigned to any variables where the respondent did not know the answer
	- `NIU (not in universe)`: Assigned to any variable where the unit (in this case, household) is not in the universe/are not eligible to answer the question

- To handle missing data:
	- Any entry falling in any of the missing data category outlined above is recoded as `NA` 
	- All variables with at least $30\%$ missing values are marked `Yes (miss_over30percent)` and may be excluded


\vspace*{2cm}
****


```{r}
miss_df2 <- (miss_df
	%>% arrange(total_prop, desc(miss_over30percent))
)
datatable(miss_df2, options = list(pageLength = 50), rownames = FALSE)
```

\vspace*{2cm}
****

- The table below shows the percentage of missingness per case. Complete cases used for analysis are `r miss_percase_df$Freq[miss_percase_df$Var1==0]`, representing `r percent(miss_percase_df$Freq[miss_percase_df$Var1==0]/sum(miss_percase_df$Freq))` of all the cases ($2006 - 2015$).

```{r}
colnames(miss_percase_df) <- c("Percent miss per case", "Number of cases")
datatable(miss_percase_df, rownames = FALSE)
```

\vspace*{2cm}
****


\vspace*{2cm}
****

```{r}
tab_freq <- (as.data.frame(miss_peryear_df)
	%>% tidyr::spread(Var2, Freq)
	%>% select(-c("2002", "2003", "2004", "2005"))
	%>% data.table::setnames("Var1", "Percent Miss")
)
datatable(tab_freq, options = list(pageLength = 20), rownames = FALSE)
```

\vspace*{2cm}
****

## Multiple interviews per household per year

- According to APHRC, there should be only 1 interview per household per year. However, we found a few cases which had multiple interviews. See the table below


```{r}
tab_freq <- (as.data.frame(tab_intperyear)
	%>% data.table::setnames(c("Var1", "Freq"), c("Interviews per HH per year", "Total"))
)
datatable(tab_freq, options = list(pageLength = 20), rownames = FALSE)
```

\vspace*{2cm}
****

- In households where there are more than 1 interviews, we select the last interview based on interview date.


