---
title: 'Report: Variables for analysis'
author: "Steve and Jonathan"
date: " `r as.Date(Sys.time())` "
output:
  html_document:
    fig_caption: yes
---


```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = FALSE
	, warning = FALSE
	, message = FALSE
	, fig.width = 10
	, fig.height = 10
	, fig.align="center"
	, results = "asis")
options(width = 12)

library(ggplot2)
theme_set(theme_bw() +
	theme(panel.spacing=grid::unit(0,"lines")))

library(forcats)
library(ggpubr)

library(dplyr)
library(DT)
library(scales)
library(dotwhisker)
library(ggstance)
library(corrplot)
library(lme4)
library(splines)

load("materials_tables.rda")
load("analysis_variables.rda")
load("overall_missing_tables.rda")
load("washdataInspect_plots.rda")
load("descriptive_stats.rda")
source("funs/ggplot_theme.R"); ggtheme()

```


## Missing data

- Questions checked for valid NIUs:
	- A follow up question with particular skip pattern
	- Expenditure questions recoded to zero
- Invalid NIUs (does not fall in any above) recoded to NA
- Don't knows and refused to answer all recoded to NAs:

- Table below summarizes variables (those with more than 10\% missing already excluded) to be used for the analysis and the missingness proportions after the corrections above.

\vspace*{2cm}
****

```{r}
datatable(var_groups_df, options = list(pageLength = 50), rownames = FALSE)
```

\vspace*{2cm}
****


## Complete cases

- A total of `r nint_all` were done between $2006 - 2015$.
- There are `r nhhid` households, interviewed in at least one of the interview years.
- Complete cases for analysis are `r nint_all`, representing `r percent(miss_percase_df$Freq[miss_percase_df$Var1==0]/sum(miss_percase_df$Freq))` of all the cases ($2006 - 2015$).

```{r}
colnames(miss_percase_df) <- c("Percent miss per case", "Number of cases")
datatable(miss_percase_df, rownames = FALSE)
```

\vspace*{2cm}
****

## Variable categorization

### Floor material

```{r}
colnames(floor_labs) <- c("old", "new")
datatable(floor_labs %>% arrange(desc(new)))
```

### Roof material

```{r}
colnames(roof_labs) <- c("old", "new")
datatable(roof_labs %>% arrange(desc(new)))
```

### Wall material

```{r}
colnames(wall_labs) <- c("old", "new")
datatable(wall_labs %>% arrange(desc(new)))
```

### Cooking material

```{r}
colnames(cook_labs) <- c("old", "new")
datatable(cook_labs %>% arrange(desc(new)))
```

### Lighting material

```{r}
colnames(light_labs) <- c("old", "new")
datatable(light_labs %>% arrange(desc(new)))
```

### Rented or owned

```{r}
colnames(rent_labs) <- c("old", "new")
datatable(rent_labs %>% arrange(desc(new)))
```

## Descriptives

**Raw percentages for all the variables** - Missing cases already dropped

-	[Click here to open](./descriptive_stats.Rout.pdf)

## Derived predictors

**Dwelling index**:

- **PCA**: [Click here to open](./dwelling_pca_plot.Rout.pdf)

**Ownership index**

- **Logistic PCA**: [Click here to open](./ownership_lpca_plot.Rout.pdf)

- **Gaussian PCA**: [Click here to open](./ownership_gpca_plot.Rout.pdf)

**Total expenditure**

- **Summation**: [Click here to open](./expenditure_index_plot.Rout.pdf)


**Problems/shocks**

- **Summation**: [Click here to open](./problems_index_plot.Rout.pdf)


